Bridging Gaps: Investigating COVID-19's Influence on Health Disparities in Connecticut

### 2023-12-15 manuscript/manuscript.tex
remove income and housing graphs

@@

The data will be presented in Section\ref{sec:data}

The methods are described in Section\ref{sec:meth}

The results are reported in Section\ref{sec:resu}

A discussion concludes in Section\ref{sec:disc}

@@

In this study, descriptive statistics is utilized to outline the total population, racial composition, 
education levels, and average rehospitalization rate across the 8 counties in Connecticut. ANOVA tests were 
conducted to assess the significance of the difference of the variables of median income, poverty level, health insurance, 
utilities access, and electronics access between counties and across the four years. Additional 
Tukey's HSD tests were conducted to determine the specific counties and years that have had significant differences within 
each of the variables for each county.

@@

\begin{table}[]
  \label{tab:Demographics}
  \caption{Demographics and Education Levels.}
  \resizebox{\columnwidth}{!}{%
  \begin{tabular}{lllllllllllllll}
                            &                                              &                  &                 &                   &                  &                  &                   &                &                &  &  &  &  &  \\
  \textbf{County}           &                                              & Fairfield County & Hartford County & Litchfield County & Middlesex County & New Haven County & New London County & Tolland County & Windham County &  &  &  &  &  \\
  \textbf{Total Population} &                                              & 944977           & 894465.25       & 182657.5          & 163318.25        & 858678           & 268477.75         & 151218.75      & 116608.75      &  &  &  &  &  \\
  \textbf{Race (Percent)}             & American Indian and Alaska Native race alone & 0.24             & 0.3075          & 0.2025            & 0.195            & 0.1725           & 0.605             & 0.05           & 0.565          &  &  &  &  &  \\
                            & Asian                                        & 5.2925           & 5.2925          & 1.9               & 3.0625           & 4.005            & 4.12              & 4.675          & 1.3675         &  &  &  &  &  \\
                            & Black or African American                    & 11.405           & 13.7025         & 1.83              & 5.385            & 13.34            & 5.8175            & 3.1075         & 2.33           &  &  &  &  &  \\
                            & Native Hawaiian and Pacific Islander         & 0.055            & 0.035           & 0                 & 0.005            & 0.0225           & 0.025             & 0              & 0.015          &  &  &  &  &  \\
                            & White                                        & 72.6325          & 70.67           & 92.6025           & 88.0875          & 73.2875          & 80.6175           & 88.025         & 88.8725        &  &  &  &  &  \\
  \textbf{Ethnicity (Percent)}        & Hispanic                                     & 19.53            & 17.8275         & 6.15              & 6.12             & 17.885           & 10.5              & 5.4475         & 11.6375        &  &  &  &  &  \\
  \textbf{Education (Percent)}        & Associates                                   & 20.74            & 25              & 27.9225           & 26.46            & 24.4175          & 29.2675           & 26.315         & 30.9775        &  &  &  &  &  \\
                            & Bachelor                                     & 26.53            & 21.4575         & 20.635            & 23.3325          & 18.785           & 18.3175           & 23.4075        & 14.595         &  &  &  &  &  \\
                            & Graduate Degree                              & 21.14            & 16.475          & 14.6975           & 18.4525          & 16.3425          & 15.18             & 17.865         & 9.55           &  &  &  &  &  \\
                            & HS Graduate                                  & 21.4725          & 26.7175         & 29.5875           & 26.0275          & 30.565           & 29.46             & 27.03          & 33.5125        &  &  &  &  &  \\
                            & Less the High School                         & 10.12            & 10.3525         & 7.1575            & 5.7275           & 9.8875           & 7.7725            & 5.385          & 11.365         &  &  &  &  &  \\
                            &                                              &                  &                 &                   &                  &                  &                   &                &                &  &  &  &  & 
  \end{tabular}%
  }
  \end{table}

@@

>>>>

% double spacing
\usepackage{setspace}
\doublespacing

@@

- The data will be presented in Section \ref{sec:data}

- The methods are described in Section \ref{sec:meth}

- The results are reported in Section \ref{sec:resu}

- A discussion concludes in Section \ref{sec:disc}

@@

In this study, descriptive statistics is utilized to outline the total population, racial composition, 
education levels, and average rehospitalization rate across the 8 counties in Connecticut. Chi-squared analyses were 
conducted to assess the significance of the difference of the variables of median income, poverty level, health insurance, 
utilities access, and electronics access between counties and across the four years. Additional 
Tukey's HSD tests were conducted to determine the specific counties and years that have had significant differences within 
each of the variables for each county.

@@

\begin{table}[h]
\label{tab:Demographics}
  \caption{Demographics and Education Levels for Counties 1-4}
  \resizebox{\columnwidth}{!}{%
  \begin{tabular}{lccccc}
    \toprule
    \textbf{Category} & \textbf{Fairfield County} & \textbf{Hartford County} & \textbf{Litchfield County} & \textbf{Middlesex County} \\
    \midrule
    Total Population & 944,977 & 894,465.25 & 182,657.5 & 163,318.25 \\
    Race (Percent) & & & & \\
    \quad American Indian and Alaska Native & 0.24 & 0.3075 & 0.2025 & 0.195 \\
    \quad Asian & 5.2925 & 5.2925 & 1.9 & 3.0625 \\
    \quad Black or African American & 11.405 & 13.7025 & 1.83 & 5.385 \\
    \quad Native Hawaiian and Pacific Islander & 0.055 & 0.035 & 0 & 0.005 \\
    \quad White & 72.6325 & 70.67 & 92.6025 & 88.0875 \\
    Ethnicity (Percent) & & & & \\
    \quad Hispanic & 19.53 & 17.8275 & 6.15 & 6.12 \\
    Education (Percent) & & & & \\
    \quad Associates & 20.74 & 25 & 27.9225 & 26.46 \\
    \quad Bachelor & 26.53 & 21.4575 & 20.635 & 23.3325 \\
    \quad Graduate Degree & 21.14 & 16.475 & 14.6975 & 18.4525 \\
    \quad HS Graduate & 21.4725 & 26.7175 & 29.5875 & 26.0275 \\
    \quad Less than High School & 10.12 & 10.3525 & 7.1575 & 5.7275 \\
    \bottomrule
  \end{tabular}%
  }
\end{table}

\begin{table}[h]
  \label{tab:Demographics}
  \caption{Demographics and Education Levels for Counties 5-8}
  \resizebox{\columnwidth}{!}{%
  \begin{tabular}{lcccc}
    \toprule
    \textbf{Category} & \textbf{New Haven County} & \textbf{New London County} & \textbf{Tolland County} & \textbf{Windham County} \\
    \midrule
    Total Population & 858,678 & 268,477.75 & 151,218.75 & 116,608.75 \\
    Race (Percent) & & & & \\
    \quad American Indian and Alaska Native & 0.1725 & 0.605 & 0.05 & 0.565 \\
    \quad Asian & 4.005 & 4.12 & 4.675 & 1.3675 \\
    \quad Black or African American & 13.34 & 5.8175 & 3.1075 & 2.33 \\
    \quad Native Hawaiian and Pacific Islander & 0.0225 & 0.025 & 0 & 0.015 \\
    \quad White & 73.2875 & 80.6175 & 88.025 & 88.8725 \\
    Ethnicity (Percent) & & & & \\
    \quad Hispanic & 17.885 & 10.5 & 5.4475 & 11.6375 \\
    Education (Percent) & & & & \\
    \quad Associates & 24.4175 & 29.2675 & 26.315 & 30.9775 \\
    \quad Bachelor & 18.785 & 18.3175 & 23.4075 & 14.595 \\
    \quad Graduate Degree & 16.3425 & 15.18 & 17.865 & 9.55 \\
    \quad HS Graduate & 30.565 & 29.46 & 27.03 & 33.5125 \\
    \quad Less than High School & 9.8875 & 7.7725 & 5.385 & 11.365 \\
    \bottomrule
  \end{tabular}%
  }
\end{table}

@@

\begin{table}[htbp]
  \centering
  \resizebox{\columnwidth}{!}{%
  \begin{tabular}{lllrrrr}
  \toprule
  & & & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{2}{l}{95\% Confidence} \\
  County 1(I) & County 2(J) & Mean Difference(I-J) & \multicolumn{1}{l}{Std. Error} & \multicolumn{1}{l}{Sig.} & \multicolumn{1}{l}{Lower Bound} & \multicolumn{1}{l}{Upper Bound} \\
  \midrule
  Fairfield County & Hartford County & 20565.50000* & 1883.47243 & \textbf{<.001} & 14327.6034 & 26803.3966 \\
  & Litchfield County & 14919.50000* & 1883.47243 & \textbf{<.001} & 8681.6034 & 21157.3966 \\
  & Middlesex County & 9671.75000* & 1883.47243 & \textbf{<.001} & 3433.8534 & 15909.6466 \\
  & New Haven County & 25662.75000* & 1883.47243 & \textbf{<.001} & 19424.8534 & 31900.6466 \\
  & New London County & 21456.50000* & 1883.47243 & \textbf{<.001} & 15218.6034 & 27694.3966 \\
  & Tolland County & 8705.00000* & 1883.47243 & \textbf{0.002} & 2467.1034 & 14942.8966 \\
  & Windham County & 28671.00000* & 1883.47243 & \textbf{<.001} & 22433.1034 & 34908.8966 \\
  \midrule
  Hartford County & Fairfield County & -20565.50* & 1883.47 & \textbf{<.001} & -26803.40 & -14327.60 \\
  & Litchfield County & -5646 & 1883.47 & 0.096 & -11883.90 & 591.90 \\
  & Middlesex County & -10893.75* & 1883.47 & \textbf{<.001} & -17131.65 & -4655.85 \\
  & New Haven County & 5097.25 & 1883.47 & 0.169 & -1140.65 & 11335.15 \\
  & New London County & 891 & 1883.47 & 1 & -5346.90 & 7128.90 \\
  & Tolland County & -11860.50* & 1883.47 & \textbf{<.001} & -18098.40 & -5622.60 \\
  & Windham County & 8105.50* & 1883.47 & 0.005 & 1867.60 & 14343.40 \\
  \midrule
  Litchfield County & Fairfield County & -14919.50* & 1883.47 & \textbf{<.001} & -21157.40 & -8681.60 \\
  & Hartford County & 5646 & 1883.47 & 0.096 & -591.90 & 11883.90 \\
  & Middlesex County & -5247.75 & 1883.47 & 0.145 & -11485.65 & 990.15 \\
  & New Haven County & 10743.25* & 1883.47 & \textbf{<.001} & 4505.35 & 16981.15 \\
  & New London County & 6537 & 1883.47 & 0.035 & 299.10 & 12774.90 \\
  & Tolland County & -6214.5 & 1883.47 & 0.051 & -12452.40 & 23.40 \\
  & Windham County & 13751.50* & 1883.47 & \textbf{<.001}  & 7513.60 & 19989.40 \\
  \midrule
  Middlesex County & Fairfield County & -9671.75* &  & 1883.47 & <.001 & -15909.65 & -3433.85 \\
  & Hartford County & 10893.75* & 1883.47 & <.001 & 4655.85 & 17131.65 \\
  & Litchfield County & 5247.75 & 1883.47 & 0.145 & -990.15 & 11485.65 \\
  & New Haven County & 15991.00* & 1883.47 & <.001 & 9753.10 & 22228.90 \\
  & New London County & 11784.75* & 1883.47 & <.001 & 5546.85 & 18022.65 \\
  & Tolland County & -966.75 & 1883.47 & 0.999 & -7204.65 & 5271.15 \\
  & Windham County & 18999.25* & 1883.47 & <.001 & 12761.35 & 25237.15 \\
  \midrule
  New Haven County & Fairfield County & -25662.75* &  & 1883.47 & <.001 & -31900.65 & -19424.85 \\
  & Hartford County & -5097.25 & 1883.47 & 0.169 & -11335.15 & 1140.65 \\
  & Litchfield County & -10743.25* & 1883.47 & <.001 & -16981.15 & -4505.35 \\
  & Middlesex County & -15991.00* & 1883.47 & <.001 & -22228.90 & -9753.10 \\
  & New London County & -4206.25 & 1883.47 & 0.368 & -10444.15 & 2031.65 \\
  & Tolland County & -16957.75* & 1883.47 & <.001 & -23195.65 & -10719.85 \\
  & Windham County & 3008.25 & 1883.47 & 0.747 & -3229.65 & 9246
  \midrule
  New London County & Fairfield County & -21456.50* & 1883.47 & <.001 & -27694.40 & -15218.60 \\
  & Hartford County & -891 & 1883.47 & 1 & -7128.90 & 5346.90 \\
  & Litchfield County & -6537.00* & 1883.47 & 0.035 & -12774.90 & -299.10 \\
  & Middlesex County & -11784.75* & 1883.47 & <.001 & -18022.65 & -5546.85 \\
  & New Haven County & 4206.25 & 1883.47 & 0.368 & -2031.65 & 10444.15 \\
  & Tolland County & -12751.50* & 1883.47 & <.001 & -18989.40 & -6513.60 \\
  & Windham County & 7214.50* & 1883.47 & 0.016 & 976.60 & 13452.40 \\
  \midrule
  Tolland County & Fairfield County & -8705.00* & 1883.47 & 0.002 & -14942.90 & -2467.10 \\
  & Hartford County & 11860.50* & 1883.47 & <.001 & 5622.60 & 18098.40 \\
  & Litchfield County & 6214.50 & 1883.47 & 0.051 & -23.40 & 12452.40 \\
  & Middlesex County & 966.75 & 1883.47 & 0.999 & -5271.15 & 7204.65 \\
  & New Haven County & 16957.75* & 1883.47 & <.001 & 10719.85 & 23195.65 \\
  & New London County & 12751.50* & 1883.47 & <.001 & 6513.60 & 18989.40 \\
  & Windham County & 19966.00* & 1883.47 & <.001 & 13728.10 & 26203.90 \\
  \midrule
  Windham County & Fairfield County & -28671.00* &  & 1883.47 & <.001 & -34908.90 & -22433.10 \\
  & Hartford County & -8105.50* & 1883.47 & 0.005 & -14343.40 & -1867.60 \\
  & Litchfield County & -13751.50* & 1883.47 & <.001 & -19989.40 & -7513.60 \\
  & Middlesex County & -18999.25* & 1883.47 & <.001 & -25237.15 & -12761.35 \\
  & New Haven County & -3008.25 & 1883.47 & 0.747 & -9246.15 & 3229.65 \\
  & New London County & -7214.50* & 1883.47 & 0.016 & -13452.40 & -976.60 \\
  & Tolland County & -19966.00* & 1883.47 & <.001 & -26203.90 & -13728.10 \\
  \end{tabular}%
  }
\end{table}
